---
title: 'Denosumab trial: primary outcome analysis'
output:
  html_document:
    toc: yes
    df_print: paged
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, comment="")
```

# Dataset

Dataset: "AnalysisDataset_Primary_secondary.xlsx"
Sheet: "Primary_GUSS"

First 5 patients:




```{r }
library(readxl)
Dataset_GUSS <- read_excel("Data/AnalysisDataset_Primary_secondary.xlsx", sheet="Primary_GUSS_Long")

library(knitr)
kable(Dataset_GUSS[Dataset_GUSS$ID %in% c(1:5),-c(1:3,11)], row.names=FALSE)

Dataset_GUSS$TREATMENT <- factor (Dataset_GUSS$TREATMENT, levels=c("placebo", "denosumab"))
Dataset_GUSS$total.GUSS <- as.numeric(Dataset_GUSS$total.GUSS)
Dataset_GUSS$time <- Dataset_GUSS$t 
Dataset_GUSS$ID_joint <- factor(Dataset_GUSS$ID_joint)

```
```{r }

Primary_GUSS_GEE <-read_excel("Data/AnalysisDataset_Primary_secondary.xlsx", sheet="Primary_GUSS_GEE")
Primary_GUSS_GEE$total.GUSS <- as.numeric(Primary_GUSS_GEE$total.GUSS)
```

```{r }
nD <- length(unique(Primary_GUSS_GEE$ID[Primary_GUSS_GEE$TREATMENT=="denosumab"]))
nP <- length(unique(Primary_GUSS_GEE$ID[Primary_GUSS_GEE$TREATMENT=="placebo"]))
```

Number of patients in the Denosumab group: `r nD`.  
Number of patients in the Placebo group: `r nP`.  

# Descriptive  

Visualization of the primary outcome by time and group:  




```{r}

cols <- c("denosumab"="#CC3333", "placebo"= "#6495ED")

Dataset_GUSS$Treatment <- Dataset_GUSS$TREATMENT

library(ggplot2)
plot <- ggplot(Dataset_GUSS, aes(x=t, y=total.GUSS, fill=Treatment)) + geom_boxplot()+
  theme_bw()+theme( axis.title.y = element_text(size = 10))+ scale_fill_manual(values=cols)+
  labs(x="", y="Total GUSS")

plot
```


Numerical summary for total.GUSS at baseline:  


```{r }

library(tidyverse)
BL<- Dataset_GUSS %>% group_by( TREATMENT) %>% filter (time=="W0") %>% summarize (n=n(),mean=mean(total.GUSS), sd=sd(total.GUSS), median=median(total.GUSS), p25=quantile(total.GUSS, probs=0.25), p75=quantile(total.GUSS, probs=0.75), min=min(total.GUSS), max=max(total.GUSS))

BL <- as.data.frame(BL)
kable(BL)
```


Numerical summary for total.GUSS at W24:  


```{r }

library(tidyverse)
BL<- Dataset_GUSS %>% group_by( TREATMENT) %>% filter (time=="W24") %>% summarize (mean=mean(total.GUSS, na.rm=TRUE), sd=sd(total.GUSS, na.rm=TRUE), median=median(total.GUSS, na.rm=TRUE), p25=quantile(total.GUSS, probs=0.25, na.rm=TRUE), p75=quantile(total.GUSS, probs=0.75, na.rm=TRUE), min=min(total.GUSS, na.rm=TRUE), max=max(total.GUSS, na.rm=TRUE))

BL <- as.data.frame(BL)
kable(BL)
```



Numerical summary for total.GUSS at W48:  

```{r }

library(tidyverse)
BL<- Dataset_GUSS %>% group_by( TREATMENT) %>% filter (time=="W48") %>% summarize (mean=mean(total.GUSS, na.rm=TRUE), sd=sd(total.GUSS, na.rm=TRUE), median=median(total.GUSS, na.rm=TRUE), p25=quantile(total.GUSS, probs=0.25, na.rm=TRUE), p75=quantile(total.GUSS, probs=0.75, na.rm=TRUE), min=min(total.GUSS, na.rm=TRUE), max=max(total.GUSS, na.rm=TRUE))

BL <- as.data.frame(BL)
kable(BL)
```



```{r , include=FALSE}

Dataset_GUSS$diff.total.GUSS.baseline <- Dataset_GUSS$total.GUSS - Dataset_GUSS$W0.total.GUSS


```


Visualization differences baseline versus W24 (W24-baseline):  

```{r }




library(ggplot2)
Dataset_GUSSdiff24 <- Dataset_GUSS[Dataset_GUSS$time=="W24",]
ggplot(Dataset_GUSSdiff24, aes(y=diff.total.GUSS.baseline,  x=TREATMENT))+geom_boxplot(outlier.shape=NA)+ geom_dotplot(binaxis='y', stackdir='center', dotsize=0.5)+theme_bw()




```

Visualization differences baseline versus W48  (W48 -baseline):  

```{r }


library(ggplot2)
Dataset_GUSSdiff48 <- Dataset_GUSS[Dataset_GUSS$time=="W48",]
ggplot(Dataset_GUSSdiff48, aes(y=diff.total.GUSS.baseline,  x=TREATMENT))+geom_boxplot(outlier.shape=NA)+ geom_dotplot(binaxis='y', stackdir='center', dotsize=0.5)+theme_bw()



```

```{r }
diffdf <- rbind (Dataset_GUSSdiff24, Dataset_GUSSdiff48 )
```

Differences with baseline at W24 and W48:  

```{r }


library(ggplot2)
ggplot(diffdf, aes(y=diff.total.GUSS.baseline, x=time, col=TREATMENT))+geom_boxplot()+theme_bw()


```




# Statistical Analysis  
## GEE analysis primary outcome with multiple imputation (SAP)   



```{r }

Primary_GUSS_GEE$TREATMENT <- factor (Primary_GUSS_GEE$TREATMENT, levels=c("placebo", "denosumab"))
Primary_GUSS_GEE$Inflammation <- factor (Primary_GUSS_GEE$inflammation, levels=c("0","1"))
Primary_GUSS_GEE$ID_joint <- factor (Primary_GUSS_GEE$ID_joint)
```


Missing value after the last available visit
or questionnaire or assessment due to dropping out the study for any reason will be
imputed.
The predictors used for the imputation model will be: randomization group,
baseline value and values at other time points available, presence of baseline inflammation (if analyses
on ‘joint level’), baseline number of affected joints (S, J, E, E/R).

Remark:  
presence of baseline inflammation was not in the imputation model, because of missing values. 



Changes in GUSS were analyzed at joint level with generalized estimating equations
(GEE), accounting for within-patient clustering. Robust standard errors will be used and
the working correlation structure specified exchangeable. Data from time
points W24 and W48 were used. The independent variables included in the model are treatment group,
visit number (categorical), interaction between treatment group and visit number, and the
baseline value of the dependent variable (continuous).
If unbalances of demographic variables were found at baseline sensitivity analysis will
be performed for the primary analysis by adding the variables for which an unbalance was
found as a covariate to the model. 

```{r, include=FALSE }
library(geepack)
library(mitml)

Primary_GUSS_GEE <- arrange(Primary_GUSS_GEE,ID_joint)
write.csv2 (Primary_GUSS_GEE [, c("ID", "ID_joint", "TREATMENT", "t", "W0.total.GUSS", "nr.of.affected.joints.baseline","total.GUSS")], "Data primary endpoint.csv")
Primary_GUSS_GEE$time2<- factor (Primary_GUSS_GEE$t, levels=c( "W48", "W24"))
#https://stackoverflow.com/questions/41570632/exporting-pooled-gee-estimates-from-the-mi-package
#imputation
fml <- total.GUSS~ 1 + t  + TREATMENT + W0.total.GUSS + nr.of.affected.joints.baseline +  (1|ID_joint)


set.seed(123)
imp <- panImpute(data = Primary_GUSS_GEE, formula=fml, n.burn=10000, n.iter=500, m=1000)

implist <- mitmlComplete(imp, "all")

# fit GEE
fit <- with(implist, geeglm(total.GUSS ~ 1 + t + TREATMENT + t*TREATMENT + W0.total.GUSS, id=as.factor(ID_joint), std.err='san.se', corstr="exchangeable"))

# define missing vcov() function for geeglm-objects
vcov.geeglm <- function(x) summary(x)$cov.scaled

# combine estimates using Rubin's rules
a<-testEstimates(fit)
```




```{r }
b <- round(a$estimates,4)
kable(b[, -c(4,6,7)])

```

Interpretation: For the same baseline measurement, the total GUSS is estimated to be `r b [3,1]` (95% CI: `r b [3,1]-2*b[3,2]` to `r b [3,1]+2*b[3,2]`) higher in the denosumab group compared to the placebo group at W24. The change of W24 versus baseline differs significantly between placebo and denosumab (p = `r b [3,5]`).  

Same model with different parametrization (reference level for time is now "W48"):  



```{r, include=FALSE }




library(geepack)
library(mitml)


#https://stackoverflow.com/questions/41570632/exporting-pooled-gee-estimates-from-the-mi-package
#imputation


# fit GEE
fit <- with(implist, geeglm(total.GUSS ~ 1 + time2 + TREATMENT + time2*TREATMENT + W0.total.GUSS, id=as.factor(ID_joint), std.err='san.se', corstr="exchangeable"))

# define missing vcov() function for geeglm-objects
vcov.geeglm <- function(x) summary(x)$cov.scaled

# combine estimates using Rubin's rules
a<-testEstimates(fit)
```

```{r }
c <- round(a$estimates,4)
kable(c[, -c(4,6,7)])

```



Interpretation: For the same baseline measurement, the total GUSS is estimated to be `r c [3,1]` (95% CI: `r c [3,1]-2*c[3,2]` to `r c [3,1]+2*c[3,2]`) higher in the denosumab group compared to the placebo group at W48. The change of W48 versus baseline differs significantly between placebo and denosumab (p = `r c [3,5]`). 




### Analysis with centered baseline value to obtain baseline adjusted mean (SE) GUSS .

To obtain the estimated mean at W24 and W48 and the corresponding SE, the same analysis as above was performed, but using the centered baseline values of GUSS, to obtain a relevant intercept.


```{r, include=FALSE }
library(geepack)
library(mitml)

Primary_GUSS_GEE <- arrange(Primary_GUSS_GEE,ID_joint )
Primary_GUSS_GEE$time2<- factor (Primary_GUSS_GEE$t, levels=c( "W48", "W24"))
Primary_GUSS_GEE$TREATMENT2<- factor (Primary_GUSS_GEE$TREATMENT, levels=c( "denosumab", "placebo"))
Primary_GUSS_GEE$W0.total.GUSS_c <- Primary_GUSS_GEE$W0.total.GUSS- mean(Primary_GUSS_GEE$W0.total.GUSS,na.rm=T)
#https://stackoverflow.com/questions/41570632/exporting-pooled-gee-estimates-from-the-mi-package
#imputation
fml <- total.GUSS~ 1 + t  + TREATMENT + W0.total.GUSS_c + nr.of.affected.joints.baseline +  (1|ID_joint)


set.seed(123)
imp <- panImpute(data = Primary_GUSS_GEE, formula=fml, n.burn=10000, n.iter=500, m=1000)

implist <- mitmlComplete(imp, "all")
```


```{r, include=FALSE }
# fit GEE
fit <- with(implist, geeglm(total.GUSS ~ 1 + t + TREATMENT + t*TREATMENT + W0.total.GUSS_c, id=as.factor(ID_joint), std.err='san.se', corstr="exchangeable"))

# define missing vcov() function for geeglm-objects
vcov.geeglm <- function(x) summary(x)$cov.scaled

# combine estimates using Rubin's rules
a<-testEstimates(fit)
```



```{r }
b <- round(a$estimates,4)
kable(b[, -c(4,6,7)])

```

Interpretation: For the same baseline measurement, the total GUSS is estimated to be `r b [3,1]` (95% CI: `r b [3,1]-2*b[3,2]` to `r b [3,1]+2*b[3,2]`) higher in the denosumab group compared to the placebo group at W24. The change of W24 versus baseline differs significantly between placebo and denosumab (p = `r b [3,5]`).  

Same model with different parametrization (reference level for time is now "W48"):  



```{r, include=FALSE }




library(geepack)
library(mitml)


#https://stackoverflow.com/questions/41570632/exporting-pooled-gee-estimates-from-the-mi-package
#imputation


# fit GEE
fit <- with(implist, geeglm(total.GUSS ~ 1 + time2 + TREATMENT + time2*TREATMENT + W0.total.GUSS_c, id=as.factor(ID_joint), std.err='san.se', corstr="exchangeable"))

# define missing vcov() function for geeglm-objects
vcov.geeglm <- function(x) summary(x)$cov.scaled

# combine estimates using Rubin's rules
a<-testEstimates(fit)
```

```{r }
c <- round(a$estimates,4)
kable(c[, -c(4,6,7)])

```



reference levels denosumab and W24 :  

```{r, include=FALSE }
# fit GEE
fit <- with(implist, geeglm(total.GUSS ~ 1 + t + TREATMENT2 + t*TREATMENT2 + W0.total.GUSS_c, id=as.factor(ID_joint), std.err='san.se', corstr="exchangeable"))

# define missing vcov() function for geeglm-objects
vcov.geeglm <- function(x) summary(x)$cov.scaled

# combine estimates using Rubin's rules
a<-testEstimates(fit)
```

```{r }
c <- round(a$estimates,4)
kable(c[, -c(4,6,7)])

```

reference levels denosumab and W48 : 

```{r, include=FALSE }
# fit GEE
fit <- with(implist, geeglm(total.GUSS ~ 1 + time2 + TREATMENT2 + time2*TREATMENT2 + W0.total.GUSS_c, id=as.factor(ID_joint), std.err='san.se', corstr="exchangeable"))

# define missing vcov() function for geeglm-objects
vcov.geeglm <- function(x) summary(x)$cov.scaled

# combine estimates using Rubin's rules
a<-testEstimates(fit)
```


```{r }
c <- round(a$estimates,4)
kable(c[, -c(4,6,7)])

```

## GEE analysis primary outcome with BOCF (senstivity analysis)   





Missing value after the last available visit
or questionnaire or assessment due to dropping out the study for any reason were imputed with the baseline value (BOCF)

Changes in GUSS were analyzed at joint level with generalized estimating equations
(GEE), accounting for within-patient clustering. Robust standard errors will be used and
the working correlation structure specified exchangeable. Data from time
points W24 and W48 were used. The independent variables included in the model are treatment group,
visit number (categorical), interaction between treatment group and visit number, and the
baseline value of the dependent variable (continuous).

```{r}
#imputation: create  total.GUSS_BOCF
Primary_GUSS_GEE$total.GUSS_BOCF <-Primary_GUSS_GEE$total.GUSS

Primary_GUSS_GEE$total.GUSS_BOCF [is.na(Primary_GUSS_GEE$total.GUSS)] <-Primary_GUSS_GEE$W0.total.GUSS [is.na(Primary_GUSS_GEE$total.GUSS)]

Primary_GUSS_GEE <- Primary_GUSS_GEE %>% arrange(ID_joint)

kable(Primary_GUSS_GEE[Primary_GUSS_GEE$ID_joint %in% c("19_LiD4", "33_ReD2"), c("ID_joint", "t", "W0.total.GUSS", "total.GUSS", "total.GUSS_BOCF")])
```

Visualization of the primary outcome by time and group without imputation:  

```{r }


library(ggplot2)
ggplot(Primary_GUSS_GEE, aes(y=total.GUSS, x=t, col=TREATMENT))+geom_boxplot()+theme_bw()


```

Visualization of the primary outcome by time and group after BOCF imputation:  

```{r }


library(ggplot2)
ggplot(Primary_GUSS_GEE, aes(y=total.GUSS_BOCF, x=t, col=TREATMENT))+geom_boxplot()+theme_bw()


```




```{r}
library(geepack)



Primary_GUSS_GEE$time1<- factor (Primary_GUSS_GEE$t, levels=c( "W24","W48"))
Primary_GUSS_GEE$time2<- factor (Primary_GUSS_GEE$t, levels=c( "W48", "W24"))
#https://stackoverflow.com/questions/41570632/exporting-pooled-gee-estimates-from-the-mi-package
#imputation

# fit GEE
fit <- with(Primary_GUSS_GEE, geeglm(total.GUSS_BOCF ~ 1 + time1 + TREATMENT + time1*TREATMENT + W0.total.GUSS, id=factor(ID_joint), std.err='san.se', corstr="exchangeable"))

# define missing vcov() function for geeglm-objects
vcov.geeglm <- function(x) summary(x)$cov.scaled



b <-round (summary(fit)$coefficients, 4)
kable(b)

```


Interpretation: For the same baseline measurement, the total GUSS is estimated to be `r b [3,1]` (95% CI: `r b [3,1]-2*b[3,2]` to `r b [3,1]+2*b[3,2]`) higher in the denosumab group compared to the placebo group at W24. The change of W24 versus baseline differs significantly between placebo and denosumab (p = `r b [3,4]`).  

  



Same model with different parametrization (reference level for time is now "W48"): 

```{r}
library(geepack)


# fit GEE
fit2 <- with(Primary_GUSS_GEE, geeglm(total.GUSS_BOCF ~ 1 + time2 + TREATMENT + time2*TREATMENT + W0.total.GUSS, id=factor(ID_joint), std.err='san.se', corstr="exchangeable"))

# define missing vcov() function for geeglm-objects
vcov.geeglm <- function(x) summary(x)$cov.scaled


b2 <-round (summary(fit2)$coefficients, 4)
kable(b2)

```

Interpretation: For the same baseline measurement, the total GUSS is estimated to be `r b2 [3,1]` (95% CI: `r b2 [3,1]-2*b2[3,2]` to `r b2 [3,1]+2*b2[3,2]`) higher in the denosumab group compared to the placebo group at W48. The change of W48 versus baseline differs significantly between placebo and denosumab (p = `r b2 [3,4]`).  



### Estimated means:

Estimated means and 95% CI for a baseline measurement of total.GUSS equal to `r mean(Primary_GUSS_GEE$W0.total.GUSS , na.rm=TRUE)`:

```{r}
library(emmeans)
means <- emmeans(fit2, specs=c("TREATMENT", "time2" ))
meanss <- as.data.frame(means)[ , c(1:3,6,7)]
kable(meanss)

```

## Linear mixed model total.GUSS  (Sensitivity analysis suggested by the statistical reviewer)

A three-level linear mixed model with patient ID and joint ID as random effects and total GUSS at baseline, treatment, time (W24 and W48)and the interaction between time and treatment as fixed effects was applied.

```{r}
library(lmerTest)
fitmm <- lmer(total.GUSS ~ 1 + time1 + TREATMENT + time1*TREATMENT + W0.total.GUSS + (1|ID_joint) + (1|ID), data=Primary_GUSS_GEE)

summary(fitmm)
```

Estimated coefficients:  

```{r}
COEF <- cbind(summary(fitmm)$coefficients,confint (fitmm)[4:8,])
kable(COEF[,-c(2,3,4)])
est24 <- COEF[3,1]
LL24 <- COEF[3,6]
UL24 <- COEF[3,7]
p24 <- COEF[3,5] 
```

W48 as reference level

```{r}

fitmm48 <- lmer(total.GUSS ~ 1 + time2 + TREATMENT + time2*TREATMENT + W0.total.GUSS + (1|ID_joint) + (1|ID), data=Primary_GUSS_GEE)

```


```{r}
COEF <- cbind(summary(fitmm48)$coefficients,confint (fitmm48)[4:8,])
kable(COEF[,-c(2,3,4)])
est48 <- COEF[3,1]
LL48  <- COEF[3,6]
UL48  <- COEF[3,7]
p48  <- COEF[3,5] 
```

As a senstivity analysis, a three-level linear mixed model with patient ID and joint ID as random effects and total GUSS at baseline, treatment, time (W24 and W48)and the interaction between time and treatment as fixed effects was applied. The estimated difference in change between W0 and W24 was `r est24` (95%CI: `r LL24` to `r UL24`; p-value= `r p24`).The estimated difference in change between W0 and W48 was `r est48` (95%CI: `r LL48` to `r UL48`; p-value= `r p48`).


